Review of Edge Detectors

### 2015-02-13 review/third_round/review_answer_4.tex

\documentclass[a4paper,10pt]{report}

\usepackage[english]{babel}
%\usepackage[none]{hyphenat}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[pdftex]{hyperref}
%\usepackage[tight,scriptsize]{subfigure}
%\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
\usepackage{jfc}
\hypersetup{hypertexnames, plainpages=false,colorlinks=true}
\usepackage{amsmath}

% Title Page
\title{}
\author{}

\usepackage{xr}
\externaldocument{../../edge-detection-review-3rd-revision-v3}
\reversemarginpar

\newcounter{myquestion}
\newcommand{\ml}{\mathcal{L}}
\newcommand{\ms}{\mathcal{S}}

\begin{document}
\maketitle

%\begin{abstract}
%\end{abstract}

\chapter{Introduction}
In this communication we answer to the fourth round of review of the article "A review of Classic edge detectors", submitted to the Image Processing Online Journal.
In the first place, we would like to thank again the reviewers for the detailed and thoughtful review provided. In the following we address the issues raised by the reviewers. For each issue, an answer is provided and a cross-reference with a red tag $C_n$ (where n is the number of the correction) to the corresponding (corrected) part of the paper is provided. In addition, changes made to the paper are highlighted in red (when significative) in the new version of the paper. 
These red marks will be removed for the final version.

The remarks from the reviewers are marked with the tag \textcolor{blue}{QUESTION} and our answers with the tag \ans.

%\section{Brief summary of changes}
\section{General changes}
\begin{itemize}
 \item Improved instructions in makefile to compile in OSX (libpng headers not found)
 \item Quality of all synthetic images (kernels) has been improved (See corrections \ref{math:common:gauss},\ref{math:common:log} and \ref{math:common:comparison})

\end{itemize}

\chapter{Answers to reviewer \#1}

\que I think the paper scientific content is now ready.\\

\que Apart from that, I had some problems with an experiment (see below) and I
think the authors did not follow the reviewers advice to reread the paper.
There were numerous grammatical errors, as well as typos or presentation
problems, which could have been easily avoided and made this review very
painful.
I'll leave it to the editor to decide whether he prefers another revision or
move directly to editing.\\

\section{CODE}

\begin{verbatim}

The code compiles fine, and "make test" also works. But when I run it with
"oranges.png" it fails (tried several parameters and both prewitt and
roberts). The problem seems to happen when reading the image

 ./edges input/oranges.png -p 0.2
A review of classic edge detection algorithms
Haldo Sponton & Juan Cardelino, IPOL 2014

Input image: 0.2
Size: 140655700885148 x 140733592255632

Number of algorithms to run: 1
Error: xmalloc: out of memory
Running Prewitt, threshold=0.20"

On the other hand, the image size is ok when I don't try to run any
algorithm:
 ./edges input/oranges.png
A review of classic edge detection algorithms
Haldo Sponton & Juan Cardelino, IPOL 2014

Input image: input/oranges.png
Size: 536 x 480

Number of algorithms to run: 0

Can you check it out?

\end{verbatim}

\ans the problem is related to the order of the arguments. The input images must be the last parameter in every case. I noted that on the README.txt.\\

\que Concerning my requirement for the demo, I was not asking for an archive of
all demo results, which would be meaningless, but for each experiment an
archive containing the results of  the different detections instead of
having to download each detection result separately.\\

\ans I agree it would be useful, but I propose to leave it to a future version of the demo. I think this can be done in the IPOL framework without another round of review.\\

\section{Paper}

\que Algorithm 2 why not merge lines 7-8?\\

\ans done.\\

Then a list of errors (again). AGAIN I did not write all mistakes down, so I
strongly encourage you to proofread your paper.\\

\que abstract: results obtained from a qualitative point of view... -> rephrase\\
\ans rephrased.\\

\que p1: "operations operations"\\
\ans done\\

\que p1: two footnotes with the same url address.\\
\ans corrected.\\

\que p2: "a disconnected an unordered "???\\
\ans corrected.\\

\que p4:  a slight variation of [...] difference -> rephrase, no main verb in
that sentence.\\
\ans rephrased.\\

\que p4: "their filter are" -> singular or plural?\\
\ans corrected.\\

\que p4: different thresholds lead to different results. Thicker... -> results:
thicker...\\
\ans corrected.\\

\que p5: [h!] in front of each figure.\\
\ans corrected.\\

\que p8: consists on convolving\\
\ans corrected.\\

\que p8 not only... BUT also\\
\ans rephrased.\\

\que p24: "are arise"\\
\ans corrected.\\

\que p25: ".\\
\ans corrected.\\

\que p29: "results [...] algorithms our sample images." fig 20-21-22-23\\
\ans corrected.\\

\chapter{Answers to reviewer \#2}

The comments of this reviewer were addressed in the previous version.\\

\bibliographystyle{unsrt}
\bibliography{../../tools/journal_list_short,../../tools/references,../../tools/hierarchical_segmentation}
\end{document}

### 2015-02-13 edge-detection-review-3rd-revision-v3.tex
last review

%-------------------------------------------------------------------------------
% A Review of Classic Edge Detectors - v10
% by Haldo Spontón & Juan Cardelino
% IPOL 2014
%-------------------------------------------------------------------------------

@@

\usepackage{hyperref,verbatim,graphicx,amsmath,amssymb,amssymb,dsfont}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage{sidecap}
\usepackage[hang,center]{subfigure}
\usepackage[table]{xcolor}
\usepackage{multicol}
\usepackage{listings}
\usepackage{color}
\usepackage{calc}
\usepackage{array}
%\usepackage{algorithm}
\usepackage{algorithmic}
\newtheorem{theorem}{Theorem}
\numberwithin{equation}{section}
\numberwithin{table}{section}
%\numberwithin{figure}{section}
\usepackage{marginnote}
\newcounter{mynote}% a new counter for use in margin notes
\usepackage[multidot]{grffile}
\usepackage{jfc}
\begin{document}

@@

\begin{abstract}
In this paper some of the classic alternatives for edge detection in digital images are studied. The main idea 
of edge detection algorithms is to find where abrupt changes in the intensity of an image have occurred. 
The first family of algorithms reviewed in this work uses the first derivative to find the changes of intensity, 
such as Sobel, Prewitt and Roberts. In the second reviewed family, second derivatives are used, for example in algorithms 
like Marr-Hildreth and Haralick. \\
Results obtained from a qualitative point of view (perceptual) and from a quantitative 
point of view (number of operations, execution time) are compared, considering different ways to convolve an 
image with a kernel (step required in some of the algorithms).
\end{abstract}

@@

\begin{ipolCode}
For all the algorithms reviewed, an open source C implementation is provided that can be downloaded from 
the IPOL publication of this article. An 
\href{http://dev.ipol.im/~juanc/ipol_demo/sc_edges/}{online demonstration}\footnote{\url{http://dev.ipol.im/~juanc/ipol_demo/sc_edges/}} is also available, where 
you can test and reproduce our results.
\end{ipolCode}

@@

Edge detection is one of the oldest and most basic operations operations in image processing, which is often used as a basic building block for more complex algorithms. The basic idea of edge detection is to detect abrupt changes in image intensity. 
Detecting those changes can be accomplished using first or second order derivatives. \\

In the 70's, edge detection methods were based on using small operators 
(such as Sobel masks), attempting to compute an approximation of the
first derivative of the image \cite{Gonzalez2007Digital}. Section ~\ref{sec:first} describes such algorithms 
and serves as an introduction to a more sophisticated 
analysis of the edge detection process.

@@

\myn{\label{intro:objective}}The objective of this work is to provide reproducible implementations of the abovementioned algorithms, along with a comprehensive quantitative evaluation of the behaviour algorithms with respect to the parameters. Quantitative benchmarks are outside the scope of this work and will be addressed in future work.
In addition, we will focus on low-level edge detection algorithms, which means that they will output a disconnected an unordered set of edgels (individual pixel facets where boundaries occur). Algorithms that perform edge integration into objects boundaries are of higher level of abstraction and not considered in this work.

@@

Algorithms based on first derivatives studied in this paper share a common structure, with the only difference  in the type of filtering used to compute those derivatives. Figure \ref{fig:blockdiagram1} shows a block diagram of that common structure. \\

\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{blockdiagram1.pdf}
	\caption{Block diagram of first derivative edge detection algorithms.}
	\label{fig:blockdiagram1}
\end{figure}

The usual tool to find the amplitude and direction of changes in 
intensity of an image $f$ is the gradient operator (denoted as $\nabla$), defined 
as the vector
\begin{equation}
	\nabla f = 
				\begin{bmatrix} 
					f_x \\ f_y
				\end{bmatrix}
	=				
				\begin{bmatrix} 
					\cfrac{\partial f}{\partial x} \\ \cfrac{\partial f}{\partial y} \\
				\end{bmatrix}.
\end{equation}

@@

To obtain the gradient, the partial derivatives $\partial f/\partial x$ and $\partial f/\partial y$ 
need to be computed at every pixel in the image. When dealing with digital images, numerical approximations 
of the partial derivatives are required, calculated in a neighborhood of each point. In the following,
the methods of Roberts, Prewitt and Sobel will be studied, whose main difference is how they perform this calculation.

@@

\myn{\label{first:roberts}}The Roberts edge detector was introduced in 1963 by L.G. Roberts in the context of 3D reconstrution \cite{im_proc:segmentation:roberts:1963:boundary_extraction}, and it was based on computing the first derivative of the image. The most usual approach to approximate the first derivative is to use a the first order Taylor expansion with a small value of $h$. Thus $f'(x)$ is computed as
\begin{equation}
	f'(x) \simeq \frac{f(x+h) - f(x)}{h}.\\
\end{equation}
Digital images are commonly seen as a discretization of a continuous image, where a pixel is evenly sampled on a grid. If we denote the grid sizes by $\Delta x$ and $\Delta y$, the continuous coordinates $x$  and $y$ can be written as $x=i\Delta x$ and $y=i\Delta y$. When no information about the spatial sampling is available, the size of the grid it is commonly assumed to be $\Delta x=\Delta y=1$.\\
Thus, in the discrete space the first derivative of the image is computed as:
\begin{equation}
\label{eq:roberts1}
	f_x = \frac{\partial f(x,y)}{\partial x} \cong f(i+1,j) - f(i,j)
\end{equation}
and
\begin{equation}
\label{eq:roberts2}
	f_y = \frac{\partial f(x,y)}{\partial y} \cong f(i,j+1) - f(i,j).
\end{equation}

@@

\begin{figure}[2][!h]
	\centering
	\begin{squarecells}{1}
		-1   \nline
		1  \nline
	\end{squarecells}
	\quad
	\begin{squarecells}{2}
		-1 & 1   \nline
	\end{squarecells}
	\caption{One-dimensional masks used to implement equations \ref{eq:roberts1} and \ref{eq:roberts2}.}
	\label{fig:1dmasks}
\end{figure}

\begin{figure}[1][!h]
	\centering
	\begin{squarecells}{2}
		-1 &  0  \nline
		0 & 1  \nline
	\end{squarecells}
	\quad
	\begin{squarecells}{2}
		0  & -1  \nline
		1 & 0  \nline
	\end{squarecells}
	\caption{\textit{Roberts cross-gradient} 2-D masks.}
	\label{fig:roberts}
\end{figure}

Figure \ref{fig:1dmasks} shows the simplest way to compute derivatives, but Roberts \cite{im_proc:segmentation:roberts:1963:boundary_extraction} proposes
to compute them as shown in Figure \ref{fig:roberts}. In order to use the same convolution code for all algorithms, our implementation uses $3\times3$ matrices, adding a row and a column of zeros to the matrices in Figure \ref{fig:roberts}, what produces the same result.

@@

The simplest digital approximation to the partial derivatives using masks of size $3\times3$ are obtained 
by taking the difference between the third and first rows (or columns) of the $3\times3$ region. The
difference between the third and first rows approximates the derivative in the x-direction, and 
the difference between the third and first columns approximates the derivative in the y-direction.
These approximations can be implemented by filtering the image with the two masks in Figure \ref{fig:prewitt}.
These masks are called \textit{Prewitt operators} \cite{im_proc:segmentation:prewitt:1970:object_enhancement}.

\begin{figure}[1][!h]
	\centering
	\begin{squarecells}{3}
		$-\frac{1}{3}$ 	& $-\frac{1}{3}$ 	& $-\frac{1}{3}$	\nline
		0 			& 0			& 0			\nline
		$\frac{1}{3}$ 	& $\frac{1}{3}$ 	& $\frac{1}{3}$	\nline
	\end{squarecells}
	\quad
	\begin{squarecells}{3}
		$-\frac{1}{3}$ 	& 0 	& $\frac{1}{3}$	\nline
		$-\frac{1}{3}$	& 0	& $\frac{1}{3}$	\nline
		$-\frac{1}{3}$ 	& 0 	& $\frac{1}{3}$	\nline
	\end{squarecells}
	\caption{Normalized \textit{Prewitt} 2-D masks of size $3\times3$.}
	\label{fig:prewitt}
\end{figure}

The left mask can be constructed (up to a scale factor) as the convolution of two filters: a vertical derivative 
$[-1\ 0\ 1]$ and an horizontal moving average $[1\ 1\ 1]^T$. The same reasoning could be applied to the right mask. Hence, these operators can be interpreted as the consecutive application of an horizontal low pass filter with a vertical derivative filter. Thus, they show smoothing properties in the direction orthogonal to the gradient.

@@

A slight variation of the Prewitt operators which use more weight on the central coefficients of the 
difference. It can be shown that using more weight in the center location provides better image smoothing. This
variation is implemented using masks shown in Figure \ref{fig:sobel}. These operators are called 
\textit{Sobel operators}.

\begin{figure}[1][!h]
	\centering
	\begin{squarecells}{3}
		$-\frac{1}{4}$ 	& $-\frac{1}{2}$ 	& $-\frac{1}{4}$	\nline
		0 			& 0			& 0			\nline
		$\frac{1}{4}$ 	& $\frac{1}{2}$ 	& $\frac{1}{4}$	\nline
	\end{squarecells}
	\quad
	\begin{squarecells}{3}
		$-\frac{1}{4}$ 	& 0 	& $\frac{1}{4}$	\nline
		$-\frac{1}{2}$	& 0	& $\frac{1}{2}$	\nline
		$-\frac{1}{4}$ 	& 0 	& $\frac{1}{4}$	\nline
	\end{squarecells}
	\caption{\textit{Sobel} 2-D masks of size $3\times3$.}
	\label{fig:sobel}
\end{figure}

Sobel masks can be seen (up to a  scale factor) as the convolution of a horizontal derivation mask 
$[-1\ 0\ 1]$ with a vertical smoothing filter $[1\ 2\ 1]$ (closer to a Gaussian response than Prewitt), and vice versa. 
Hence, these operators have better smoothing properties, as mentioned in the preceding paragraph. \\

The computational cost of applying Prewitt and Sobel masks is exactly the same. Thus, it is preferable to 
use Sobel operators, because edges are better localized, and their filter are also less aliased, because of the weighted shape of $[1\ 2\ 1]$.

@@

As mentioned before, edges can be seen as abrupt changes in intensity, i.e. higher values of gradient.
An example of this behavior is shown in Figure \ref{fig:profiles3d}, where gradient was computed using Sobel operators.

@@

Finally, the edges image is obtained by thresholding the gradient magnitude image, i.e. for pixel a at position $i,j$ in the image compute
\begin{equation*}
	\mbox{edges}[i,j] = \begin{cases} 1,& \mbox{if}\ M[i,j]\geq\mbox{th} \\
									0,& \mbox{if}\ M[i,j]<\mbox{th}
					  \end{cases}
\end{equation*}
where $\mbox{th}$ is the threshold. A black and white image is obtained, in which edge points are indicated in white (see Figure \ref{fig:thresholding}). 
It is noted that different thresholds lead to different results. Thicker or more edges for smaller thresholds, fewer edges 
for larger thresholds. This threshold, and the others mentioned below, are defined as a percentage of the maximum value 
of the gradient image. The advantage of this is to adapt the threshold to the dynamic range of the image. 
Therefore, the parameter $threshold$ in the algorithms takes values ​​between $0$ and $1$.

@@

The pseudo-code of implemented algorithms is shown in Algorithm \ref{algo:fded}.

@@

\begin{algorithm}[t]
\caption{First derivative edge detection algorithms.}
\label{algo:fded}
\begin{algorithmic}[1]
\REQUIRE input image, threshold $th$.
\STATE $im \leftarrow$ input image
\STATE Define $operator_x$ and $operator_y$ \COMMENT{Roberts, Prewitt or Sobel.}
\STATE $g_x \leftarrow$ convolution($im$,$operator_x$)
\STATE $g_y \leftarrow$ convolution($im$,$operator_y$)
\STATE $max_M \leftarrow 0$
\FORALL{pixel $i$ in image}
	\STATE $M[i] \leftarrow \sqrt{g_x^2+g_y^2}$ \COMMENT{Gradient magnitude.}
	\IF{$M[i]>max_M$}
		\STATE $max_M \leftarrow M[i]$
	\ENDIF
\ENDFOR
\FORALL{pixel $i$ in image}
	\IF{$M[i] \geq th \times max_M$}
		\STATE $im_{OUT}[i] \leftarrow 255$
	\ELSE
		\STATE $im_{OUT}[i] \leftarrow 0$
	\ENDIF
\ENDFOR
\RETURN output image $\leftarrow im_{OUT}$
\end{algorithmic}
\end{algorithm}

@@

The edge detection methods discussed in the previous section are simply based on filtering the 
image with different masks, without taking into account the characteristics of the edges or 
noise in the image.

\myn{\label{second:references}}The two algorithms presented in this section (Marr-Hildreth \cite{segm:edge_region:marr:84:digital_step} and Haralick \cite{bb20239}) 
are based on the second derivative of the image, and both take steps to reduce noise before 
detecting edges in the image.

@@

The Marr-Hildreth algorithm is a method of detecting edges in digital 
images. It is based on finding zero crossing points of the second derivative
of the image. This can be done in several ways. Two different ways of doing 
this are implemented in this work (see block diagram in Figure 
\ref{fig:blockdiagram2}): convolving the image with a Gaussian kernel and then 
approximating the second derivative (Laplacian) with a 3x3 kernel, or 
convolving the image with a kernel calculated as the Laplacian of a 
Gaussian function. There are more ways to do so, for example, using 
recursive Gaussian filters \cite{Deriche1993Recursively}.

@@

Some auxiliary functions are needed such as Gaussian kernel and Laplacian of a Gaussian 
kernel generation, and 2-D convolution of an image with a given kernel, 
with different boundary conditions. These operations will be discussed 
in detail in section \ref{sec:appendix1}.

@@

The Marr-Hildreth algorithm consists on convolving the input image $f(x,y)$ with a LoG kernel;
\begin{equation}\label{eq:log}
  g(x,y) = [\nabla^2G(x,y)]\star f(x,y), 
\end{equation}
and then finding the zero crossings of $g(x,y)$ to determine the location of edges in $f(x,y)$. 
Because these are linear processes, equation \ref{eq:log} can be written also as
\begin{equation}
  g(x,y) = \nabla^2[G(x,y)\star f(x,y)]
\end{equation}
indicating that the image can be smoothed with a Gaussian filter first, and then compute the Laplacian of the result\footnote{The difference between these approaches lies in the compromise between the accuracy in the calculation and the computational cost (see Section \ref{kernelcomparison}).} .

Then, generation of both Gaussian and LoG kernels is required (see section \ref{sec:appendix1}).\\

@@

A zero crossing at pixel $p$ implies that the signs of at least two opposite neighboring pixels are 
different. There are four cases to test: left/right, up/down, and the two diagonals. In this case 
a threshold is used, so that not only the signs of the opposite pixels must differ, also their 
difference in absolute value must be greater than a certain threshold.

@@

Zero crossing detection is the key feature of the Marr-Hildreth edge detection method. The technique 
presented in the previous paragraph is attractive for its simplicity of implementation and its low 
computational cost. In general it is a technique that yields good results, but if more precision in 
finding the zero crossings is needed, more advanced methods for finding zero crossings with subpixel 
accuracy could be used (e.g.\ marching squares \cite{comp_graph:surf_recon:lorensen:87:marching_cubes}).

@@

Here, the interpolation method used in the original work of Haralick is presented, although there are other options to do this \cite{getreuer}.

>>>>

%-------------------------------------------------------------------------------
% A Review of Classic Edge Detectors - v3.3
% by Haldo Spontón & Juan Cardelino
% IPOL 2015
%-------------------------------------------------------------------------------

@@

\usepackage{hyperref,verbatim,graphicx,amsmath,amssymb,amssymb,dsfont}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage{sidecap}
\usepackage[hang,center]{subfigure}
\usepackage[table]{xcolor}
\usepackage{multicol}
\usepackage{listings}
\usepackage{color}
\usepackage{calc}
\usepackage{array}
%\usepackage{algorithm}
\usepackage{algorithmic}
\newtheorem{theorem}{Theorem}
\numberwithin{equation}{section}
\numberwithin{table}{section}
%\numberwithin{figure}{section}
\usepackage{marginnote}
\newcounter{mynote}% a new counter for use in margin notes
\usepackage[multidot]{grffile}
\usepackage{jfc}

\newcommand{\demourl}{http://dev.ipol.im/~juanc/ipol_demo/sc_edges/}

\begin{document}

@@

\begin{abstract}
In this paper some of the classic alternatives for edge detection in digital images are studied. The main idea 
of edge detection algorithms is to find where abrupt changes in the intensity of an image have occurred. 
The first family of algorithms reviewed in this work uses the first derivative to find the changes of intensity, 
such as Sobel, Prewitt and Roberts. In the second reviewed family, second derivatives are used, for example in algorithms 
like Marr-Hildreth and Haralick. \\
Obtained results are analyzed from a qualitative point of view (perceptual) and from a quantitative 
point of view (number of operations, execution time), considering different ways to convolve an image with a kernel (step required in some of the algorithms).
\end{abstract}

@@

\begin{ipolCode}
For all the reviewed algorithms, an open source C implementation is provided which can be downloaded from 
the IPOL publication of this article. An 
\href{\demourl}{online demonstration}%\footnote{\url{http://dev.ipol.im/~juanc/ipol_demo/sc_edges/}} 
is also available, where you can test and reproduce our results.
\end{ipolCode}

@@

Edge detection is one of the oldest and most basic operations in image processing, which is often used as a basic building block for more complex algorithms. The basic idea of edge detection is to detect abrupt changes in image intensity. 
Detecting those changes can be accomplished using first or second order derivatives. \\

In the 70's, edge detection methods were implemented using small operators 
(such as Sobel masks), attempting to compute an approximation of the
first derivative of the image \cite{Gonzalez2007Digital}. Section \ref{sec:first} describes such algorithms 
and serves as an introduction to a more sophisticated 
analysis of the edge detection process.

@@

The objective of this work is to provide reproducible implementations of the abovementioned algorithms, along with a comprehensive quantitative evaluation of the behaviour algorithms with respect to the parameters. Quantitative benchmarks are outside the scope of this work and will be addressed in future work.
In addition, we will focus on low-level edge detection algorithms, which means that they will output a disconnected and unordered set of edgels (individual pixel facets where boundaries occur). Algorithms that perform edge integration into objects boundaries are of higher level of abstraction and not considered in this work.

@@

The algorithms based on first derivatives studied in this paper share a common structure, which only differs in the type of filtering used to compute those derivatives. Figure \ref{fig:blockdiagram1} shows a block diagram of that common structure. \\

\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{blockdiagram1.pdf}
	\caption{Block diagram of first derivative edge detection algorithms.}
	\label{fig:blockdiagram1}
\end{figure}

The usual tool to find the magnitude and direction of the
intensity changes of an image $f$ is the gradient operator (denoted as $\nabla$), defined 
as the vector
\begin{equation}
	\nabla f = 
				\begin{bmatrix} 
					f_x \\ f_y
				\end{bmatrix}
	=				
				\begin{bmatrix} 
					\cfrac{\partial f}{\partial x} \\ \cfrac{\partial f}{\partial y} \\
				\end{bmatrix}.
\end{equation}

@@

To obtain the gradient, the partial derivatives $\partial f/\partial x$ and $\partial f/\partial y$ 
need to be computed at every pixel in the image. When dealing with digital images, numerical approximations 
of these derivatives are computed in a neighborhood of each point. In the following,
the methods of Roberts, Prewitt and Sobel will be studied, whose main difference is how they perform this calculation.

@@

\myn{\label{first:roberts}}The Roberts edge detector was introduced in 1963 by L.G. Roberts in the context of 3D reconstrution \cite{im_proc:segmentation:roberts:1963:boundary_extraction}, and it was based on the computation of the first derivative of the image. The most usual approach to approximate the first derivative is to use a the first order Taylor expansion with a small value of $h$. Thus $f'(x)$ is computed as
\begin{equation}
	f'(x) \simeq \frac{f(x+h) - f(x)}{h}.\\
\end{equation}
Digital images are commonly seen as a discretization of a continuous image, where a pixel is evenly sampled on a grid. If we denote the grid sizes by $\Delta x$ and $\Delta y$, the continuous coordinates $x$  and $y$ can be written as $x=i\Delta x$ and $y=i\Delta y$. When no information about the spatial sampling is available, the size of the grid it is commonly assumed to be $\Delta x=\Delta y=1$.\\
Thus, in the discrete space the first derivative of the image is computed as:
\begin{equation}
\label{eq:roberts1}
	f_x = \frac{\partial f(x,y)}{\partial x} \cong f(i+1,j) - f(i,j)
\end{equation}
and
\begin{equation}
\label{eq:roberts2}
	f_y = \frac{\partial f(x,y)}{\partial y} \cong f(i,j+1) - f(i,j).
\end{equation}

@@

\begin{figure}[h!]
	\centering
	\begin{squarecells}{1}
		-1   \nline
		1  \nline
	\end{squarecells}
	\quad
	\begin{squarecells}{2}
		-1 & 1   \nline
	\end{squarecells}
	\caption{One-dimensional masks used to implement equations \ref{eq:roberts1} and \ref{eq:roberts2}.}
	\label{fig:1dmasks}
\end{figure}

\begin{figure}[h!]
	\centering
	\begin{squarecells}{2}
		-1 &  0  \nline
		0 & 1  \nline
	\end{squarecells}
	\quad
	\begin{squarecells}{2}
		0  & -1  \nline
		1 & 0  \nline
	\end{squarecells}
	\caption{\textit{Roberts cross-gradient} 2-D masks.}
	\label{fig:roberts}
\end{figure}

Figure \ref{fig:1dmasks} shows the simplest way to compute derivatives, but Roberts \cite{im_proc:segmentation:roberts:1963:boundary_extraction} proposes
to compute them as shown in Figure \ref{fig:roberts}. In order to use the same convolution code for all algorithms, our implementation uses $3\times3$ matrices, adding a row and a column of zeros to the matrices in Figure \ref{fig:roberts}, which produces the same result.

@@

The simplest digital approximation of the partial derivatives using masks of size $3\times3$ is obtained 
by taking the difference between the third and first rows (or columns) of the $3\times3$ region. The
difference between the third and first rows approximates the derivative in the x-direction, and 
the difference between the third and first columns approximates the derivative in the y-direction.
These approximations can be implemented by filtering the image with the two masks shown in Figure \ref{fig:prewitt}.
These masks are called \textit{Prewitt operators} \cite{im_proc:segmentation:prewitt:1970:object_enhancement}.

\begin{figure}[h!]
	\centering
	\begin{squarecells}{3}
		$-\frac{1}{3}$ 	& $-\frac{1}{3}$ 	& $-\frac{1}{3}$	\nline
		0 			& 0			& 0			\nline
		$\frac{1}{3}$ 	& $\frac{1}{3}$ 	& $\frac{1}{3}$	\nline
	\end{squarecells}
	\quad
	\begin{squarecells}{3}
		$-\frac{1}{3}$ 	& 0 	& $\frac{1}{3}$	\nline
		$-\frac{1}{3}$	& 0	& $\frac{1}{3}$	\nline
		$-\frac{1}{3}$ 	& 0 	& $\frac{1}{3}$	\nline
	\end{squarecells}
	\caption{Normalized \textit{Prewitt} 2-D masks of size $3\times3$.}
	\label{fig:prewitt}
\end{figure}

The left mask can be constructed (up to a scale factor) as the convolution of two filters: a vertical derivative 
$[-1\ 0\ 1]^T$ and an horizontal moving average $[1\ 1\ 1]$. The same reasoning could be applied to the right mask. Hence, these operators can be interpreted as the consecutive application of an horizontal low pass filter with a vertical derivative filter, and viceversa. Thus, they show smoothing properties in the direction orthogonal to the gradient.

@@

\textit{Sobel operators} are a slight variation of the Prewitt operators which use more weight on the central coefficients of the masks. It can be shown that using more weight in the center location provides better image smoothing. This variation is implemented using masks shown in Figure \ref{fig:sobel}.

\begin{figure}[h!]
	\centering
	\begin{squarecells}{3}
		$-\frac{1}{4}$ 	& $-\frac{1}{2}$ 	& $-\frac{1}{4}$	\nline
		0 			& 0			& 0			\nline
		$\frac{1}{4}$ 	& $\frac{1}{2}$ 	& $\frac{1}{4}$	\nline
	\end{squarecells}
	\quad
	\begin{squarecells}{3}
		$-\frac{1}{4}$ 	& 0 	& $\frac{1}{4}$	\nline
		$-\frac{1}{2}$	& 0	& $\frac{1}{2}$	\nline
		$-\frac{1}{4}$ 	& 0 	& $\frac{1}{4}$	\nline
	\end{squarecells}
	\caption{\textit{Sobel} 2-D masks of size $3\times3$.}
	\label{fig:sobel}
\end{figure}

Sobel masks can be seen (up to a  scale factor) as the convolution of a vertical derivation mask 
$[-1\ 0\ 1]^T$ with an horizontal smoothing filter $[1\ 2\ 1]$ (closer to a Gaussian response than Prewitt), and vice versa. 
Hence, these operators have better smoothing properties, as mentioned in the preceding paragraph. \\

The computational cost of applying Prewitt and Sobel masks is exactly the same. Thus, it is preferable to use Sobel operators, because edges are better localized, and its filters are also less aliased, because of the weighted shape of the kernel.

@@

As mentioned before, edges can be seen as abrupt changes in intensity, which correspond high values of the gradient.
An example of this behavior is shown in Figure \ref{fig:profiles3d}, where gradient was computed using Sobel operators.

@@

Finally, the edges image is obtained by thresholding the gradient magnitude image, i.e. for a pixel at position $i,j$ in the image the algorithm computes
\begin{equation*}
	\mbox{edges}[i,j] = \begin{cases} 1,& \mbox{if}\ M[i,j]\geq\mbox{th} \\
									0,& \mbox{if}\ M[i,j]<\mbox{th}
					  \end{cases}
\end{equation*}
where $\emph{th}$ is the threshold. A black and white image is obtained, in which edge points are indicated in white (see Figure \ref{fig:thresholding}). 
It is noted that different thresholds lead to different results: thicker or more edges for smaller thresholds, fewer and sparser edges for larger thresholds. This threshold, and the others mentioned below, are defined as a percentage of the maximum value 
of the gradient image. The advantage of this approach is to adapt the threshold to the dynamic range of the image. 
Therefore, the parameter $threshold$ in the algorithms takes values ​​between $0$ and $1$.

@@

The pseudo-code of the implemented algorithms is shown in Algorithm \ref{algo:fded}.

@@

\begin{algorithm}[t]
\caption{First derivative edge detection algorithms.}
\label{algo:fded}
\begin{algorithmic}[1]
\REQUIRE $im$ input image, threshold $th$.
\STATE Define $operator_x$ and $operator_y$ \COMMENT{Roberts, Prewitt or Sobel.}
\STATE $g_x \leftarrow$ convolution($im$,$operator_x$)
\STATE $g_y \leftarrow$ convolution($im$,$operator_y$)
\STATE $max_M \leftarrow 0$
\FORALL{pixel $i$ in image}
	\STATE $M[i] \leftarrow \sqrt{g_x^2+g_y^2}$ \COMMENT{Gradient magnitude.}
	\IF{$M[i]>max_M$}
		\STATE $max_M \leftarrow M[i]$
	\ENDIF
\ENDFOR
\FORALL{pixel $i$ in image}
	\IF{$M[i] \geq th \times max_M$}
		\STATE $im_{OUT}[i] \leftarrow 255$
	\ELSE
		\STATE $im_{OUT}[i] \leftarrow 0$
	\ENDIF
\ENDFOR
\RETURN output image $\leftarrow im_{OUT}$
\end{algorithmic}
\end{algorithm}

@@

The edge detection methods discussed in the previous section are simply based on filtering the 
image with different masks, without taking into account the characteristics of the edges or 
the noise in the image.

Both algorithms presented in this section (Marr-Hildreth \cite{segm:edge_region:marr:84:digital_step} and Haralick \cite{bb20239}) 
are based on the second derivative of the image, and take steps to reduce noise before 
detecting edges in the image.

@@

The Marr-Hildreth algorithm is a method of detecting edges in digital 
images. It is based on finding zero crossing points of the second derivative
of the image. This computation can be done in several ways, but in this work we implement two of these ways  (see block diagram in Figure \ref{fig:blockdiagram2}): convolving the image with a Gaussian kernel and then 
approximating the second derivative (Laplacian) with a 3x3 kernel, or 
convolving the image with a kernel calculated as the Laplacian of a 
Gaussian function. There are more ways to do perform the same tasks, for example, using 
recursive Gaussian filters \cite{Deriche1993Recursively}.

@@

IN order to implement this algorithm some auxiliary functions are needed, such as Gaussian kernel and Laplacian of a Gaussian 
kernel generation, and 2-D convolution of an image with a given kernel, 
using different boundary conditions. These operations will be discussed 
in detail in section \ref{sec:appendix1}.

@@

The main idea of Marr-Hildreth's algorithm is to convolve the input image $f(x,y)$ with a LoG kernel;
\begin{equation}\label{eq:log}
  g(x,y) = [\nabla^2G(x,y)]\star f(x,y), 
\end{equation}
and then finding the zero crossings of $g(x,y)$ to determine the location of edges in $f(x,y)$. 
Because these are linear processes, equation \ref{eq:log} can be written also as
\begin{equation}
  g(x,y) = \nabla^2[G(x,y)\star f(x,y)]
\end{equation}
indicating that the image can be smoothed with a Gaussian filter first, and then compute the Laplacian of the result\footnote{The difference between these approaches lies in the compromise between the accuracy in the calculation and the computational cost (see Section \ref{kernelcomparison}).} .

Then, the algorithm requires the generation of both Gaussian and LoG kernels (see section \ref{sec:appendix1}).\\

@@

A zero crossing at pixel $p$ implies that the signs of at least two opposite neighboring pixels are 
different. There are four cases to test: left/right, up/down, and the two diagonals. In this case 
two conditions must hold: first, the signs of the opposite pixels must differ, and second, their 
difference in absolute value must be greater than a certain threshold.

@@

Zero crossing detection is the key feature of the Marr-Hildreth edge detection method. The technique 
presented in the previous paragraph is attractive for its simplicity of implementation and its low 
computational cost. In general it yields good results, but for applications that require accurate edge localization, more advanced methods for finding zero crossings with subpixel 
accuracy could be used (e.g.\ marching squares \cite{comp_graph:surf_recon:lorensen:87:marching_cubes}).

@@

Here, we present the interpolation method used in the original work of Haralick, although there are other options to do this \cite{getreuer}.
